\documentclass[12pt]{article}

\usepackage{cal}

\begin{document}

\begin{center}
        COMMON AREA LEASE AGREEMENT\\
        BETA WPI HOUSING CORPORATION\\
        ETA TAU CHAPTER OF BETA THETA PI\\
        2021--2022 Academic Year
\end{center}

This Common Area Lease Agreement (hereafter, “Agreement”) is entered into this \today{} between the Beta WPI Housing Corporation, a Massachusetts corporation (hereafter ``Corporation''), and the Eta Tau Chapter of Beta Theta Pi (hereafter ``Chapter''), a Massachusetts unincorporated association comprised of college students (hereafter ``Chapter Members'') attending Worcester Polytechnic Institute (hereafter ``Host Institution.'')

\textbf{WHEREAS}, Corporation is the Lessee of the real property located at 52 Fruit St (hereafter ``Property''); and

\textbf{WHEREAS}, Chapter desires to utlize Common Areas, as defined below, of the Property for its operations as a chapter of Beta Theta Pi; and

\textbf{WHEREAS}, Corporation anticipates making rooms in the property available for lease to Chapter Members; and

\textbf{WHEREAS}, Chapter understands that the Chapter derives benefits from, and that Chapter Members who do not enter into individual agreements with the Corporation, but who pay dues to Chapter, derive benefits from, the use of Common Areas in and on the Property:

\textbf{NOW, THEREFORE}, Corporation and Chapter agree as follows:

\begin{enumerate}
        \item The Common Areas are leased by Corporation to Chapter. The ``Common Areas'' are defined as all areas of Property other than the rooms made available by Corporation for lease to Chapter Members, including, without limitation, the kitchens, living rooms, front and back porch, and other common rooms in the property and all furnishings located therein; the hallways, stairs, bathrooms, storage areas, passageways and similar areas; the roof, walls, exterior, porches, doors, windows, and all other structural and non-structural components of the building on the property; and the yard, grounds, and related improvements on the property.

        \item As rent under this agreement, Chapter shall pay the Corporation an Empty Bed Fee and a Parlor Fee.
                The ``Empty Bed Fee'' is owed whenever fewer than ten Chapter Members have active leases from Corporation to reside on Property (hereafter ``Room License Agreements''), and is equal to the additional rent, if any, that Corporation would have received from Chapter Members had there been ten Chapter Members with Room License Agreements.
                The ``Parlor Fee'' is owed semiannually and is equal to the total number of Chapter Members multiplied by \$(PARLOR FEE AMOUNT).
                Corporation understands that the Chapter may recoup the Empty Bed Fee and Parlor Fee by imposing fees on Chapter Members, including those who have not executed Room License Agreements, and Corporation agrees to assist the Chapter in imposing such charges, but not at  cost, expense, or liability to Corporation.
                Notwithstanding the foregoing, as between Corporation and Chapter, Chapter shall be solely and exclusively responsible for paying said Fees.

        \item The Empty Bed Fee will become due when the rent from Chapter Members which the Empty Bed Fee replaces would have become due.

        \item The Parlor Fee will become due on September 1 and January 1 of each year.

        \item No later than January 1 of each year, Chapter will provide a written list to Corporation which states the names, email addresses, phone numbers, and current and summer addresses of Chapter Members who intend to enter into Room License Agreements for the next academic year.

        \item Chapter agrees that Chapter and Chapter Members will comply with state, federal, and local laws, and the rules and regulations of Beta Theta Pi and Host Institution.
                Chapter agrees that Chapter and Chapter Members will comply with the House Rules, which may be modified by Corporation at any time with notice to Chapter.

        \item This Agreement shall continue until terminated by Corporation. Corporation has the right to terminate the Agreement:

                \begin{enumerate}[label=\alph*.]
                        \item Upon five (5) days' prior written notice by Corporation to Chapter if Chapter ceases to be a chapter in good standing with Beta Theta Pi; or

                        \item Upon twenty (20) days' prior written notice by Corporation to Chapter if Corporation, in its sole and absolute discretion, determines that it is no longer economically feasible for Corporation to rent rooms to Chapter Members; or

                        \item Upon twenty (20) days' prior written notice by Corporation to Chapter if Chapter is delinquent in any amount it owes to Corporation pursuant to this Agreement.
                \end{enumerate}

        \item Chapter agrees to maintain the Common Areas in a presentable fashion so that they are appealing to the public and potential Chapter Members.
                In the event that Chapter fails to so maintain the Common Areas, Corporation may, at its option, perform such maintenance in the place of Chapter.
                Under no circumstances shall the Chapter complete repairs or improvements to Property or contract with any outside party to have such repairs or improvements completed without the express written consent of Corporation.
                All work done to the Property must be coordinated with Corporation.
                Corporation shall be responsible for all major repairs and restoration of the Property not resulting from damage caused by Chapter or Chapter Members.
                Chapter agrees to provide to Corporation a chore plan that has been approved by the Chapter's House Manager prior to each academic year.

        \item Chapter understands and agrees that it is not an agent of Corporation, that it has no authority to make any representations on behalf of Corporation, and that it has no authority to enter into any agreement or obligation on behalf of Corporation.

        \item Corporation shall pay, on or before the date due, all costs and fees, including connection fees and deposits, related to all utility service to the Property, including, but not limited to, \st{water, sewer, drainage, gas, electric}\footnote{All utility services not paid by Corporation are paid by Property Owner}, telephone and other telecommunication service, \st{and cable television}, except to the extent that local law expressly requires that the same be paid by the ``tenant'' of the Property; provided, however, to the extent enforceable under local law, Corporation hereby expressly waives any such requirements and agrees to pay the same directly, or, if so permitted under local law, Corporation may charge such costs to Chapter as additional rent.
                \st{Corporation shall also pay all real estate taxes, assessments, governmental fees, payments and fines related to the Property, Chapter's use thereof or to the acts or omissions of Corporation}.
                Corporation shall also pay all rental fees, payments, and fines in accordance with any agreements made between Corporation and the owner of the Property.
                The foregoing shall not apply to building permits or similar approvals required due to remodeling or similar work undertaken by Corporation. Corporation shall provide Chapter with evidence of the above payments when requested by Chapter.
        \item To the extent permitted by law, Chapter agrees that Chapter itself is a party to, and bound by, this Agreement. Whereas Chapter is an unincorporated association, Chapter Members understand and agree that they are parties to, and bound by, this Agreement, and that they will be jointly and severally liable for all amounts owed to Corporation by Chapter under this Agreement.
\end{enumerate}

\clearpage
\textbf{\large Chapter}

\signature{President}

\signature{Risk Manager}

\signature{House Manager}

\clearpage
\textbf{\large Corporation}

\signature{President}

\end{document}
